quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2024-06-22 paper-quollr.Rmd
Add lift model to high-dimensions

>>>>

The final step involves lifting the fitted $2\text{-}D$ model into $p\text{-}D$ by computing the $p\text{-}D$ mean of data points within each bin to represent bin centroids. This transformation is performed using the `avg_highd_data()` function, which takes $p\text{-}D$ data and their corresponding hexagonal bin IDs as inputs.
